\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}
\title{Software and Networking infrastructure \\for IoT and Robotics collaboration}

\author{
\IEEEauthorblockN{Loic Dauphin}
\IEEEauthorblockA{
Inria, Universit\'e Paris-Saclay\\
loic.dauphin@inria.fr
}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{
Springfield, USA\\
Email: homer@thesimpsons.com
}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy}
}

\maketitle

\begin{abstract}
%\blindtext
\end{abstract}

\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Robotics/IoT collaboration}

Robots will need to collaborate to fulfill tasks that they cannot do alone at some point.
To collaborate, they need to communicate to each other their "skills" (what they can or cannot do, example : "I can move on an plane floor, but not stairs").
Once all the skills have been collected, compared with a mission statement, a mission plan can be generated.
Once the plan is generated, the controllers can execute this plan via standard communication interfaces.

In the case of robot modularity, where every robot parts can be considered as a standalone system collaborating with others to make a whole robot, this kind of system would enable hardware constructor to focus on the hardware itself.
With a proper description of the hardware skills, a robot could use a new module with no need to modify the robot's software.
This would be even mode useful if robots are able to remove/add/replace parts autonomousely.

In the case of a task that is too hard for one robot, the robot could autonomously ask the help of other robots or external sensors to reach it's goals.

The computing power needed for this kind of system is likely to be too high for being embedded, considering the complexity of missions the robots will be needed to accomplish.
There is a need to distribute the computing tasks, or (at least partly) execute it in the cloud, taking advantage of the omnipresence of wireless networking.

\section{A common communication protocol}

\subsection{Needed patterns}

\subsubsection{Discovery}

To collaborate, robots will need the help of the network to discover each other.
We need to discover the robots endpoints (named/addressed data streams) and the type of data exchanged.

The problem solver / planner part will also need to "understand" what kind of actions the robot can do.
The "skills" can be described with a specific language (PDDL, STRIPS, and co), and served by the robots to be downloaded by the planning part.

\subsubsection{Pub/Sub}

This communication pattern is used when we need the data to be sent to the consumer as fast as possible after it has bee produced.
For example, the data of a sensor that is used in a (realtime) control system.
Also, the commands of an controller that is sent to an actuator (real or virtual).

\subsubsection{Req/Res}

This communication pattern is used when the consumer need a big chunck of data, or data that is not updated often, or when requesting a computation task.
This can be used for example to serve the skills descriptions, where a planned will request only when the robot is discovered.
This can also be used to run some heavy computation on a server if the client is not powerful enough.

\subsection{The interface of each entities}

\subsubsection{Control interface (sense+act)}

ROS already have some standard sensor/actuator/navigation interfaces that can be used ?

\subsubsection{Skills/Constraints (Plan)}

\section{A "collaboration" planner}

\subsection{Expressing the mission of a robot}
\subsection{Need to discover and get information for planning from control nodes}
\subsection{Describing the environment + control/planning loop}

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

\end{document}
